comgen-outline

### 2017-06-09 paper/appendix-fullModelPosteriors.Rmd
generics prevalence distribution posterior plots

full_sentences <- mutate(md, sentence = paste(category, property, sep = "_"))$sentence

@@

d.prior.summary <- d.prior %>% 
  mutate(sentence = paste(Category, Property, sep = "_")) %>%
  filter(sentence %in% full_sentences) %>%
  mutate(prevalence = prevalence / 100) %>%
  group_by(Category, Property) %>%
  multi_boot_standard(column = "prevalence")
```

@@

Marginal distributions on prevalence
```{r}

```

@@

```{r}

  bind_rows(
    d.prior %>% 
    mutate(prevalence = prevalence / 100) %>%
    rename(property = Property) %>% 
    select(property, prevalence) %>%
    mutate(src = 'data'),
     m.samp.prevalence.prior %>%
      mutate(src = 'model')
  ) %>% ggplot(., aes( x = prevalence, color = src))+
    stat_ecdf()+
    facet_wrap(~property)+
    scale_color_solarized()+
    scale_x_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
    scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
    theme(strip.text.y = element_text(angle = 0))
```

>>>>

full_sentences <- d.gen.endorse.bayes$sentence

@@

d.prior.summary <- d.prior %>% 
  mutate(sentence = paste(Category," " ,Property, ".", sep = "")) %>%
  filter(sentence %in% full_sentences) %>%
  mutate(prevalence = prevalence / 100) %>%
  group_by(Category, Property) %>%
  multi_boot_standard(column = "prevalence")
```

```{r fig.width = 6, fig.height = 6}
bind_rows(
  d.prior %>% 
  mutate(sentence = paste(Category," " ,Property, ".", sep = "")) %>%
  filter(sentence %in% full_sentences) %>%
  mutate(prevalence = prevalence / 100,
         src = 'data') %>% 
    select(-workerid, -trial_type),
  m.samp %>% 
    filter(type == "withinKind") %>%
    select(property, category, val) %>%
    rename(Category = category, Property = property, prevalence = val) %>%
    mutate(src = 'model') 
  ) %>%
ggplot(. , aes( x = prevalence, color = src))+
  geom_density(size = 1.1, aes( y = ..scaled.. ))+
  facet_wrap(~Property + Category)+
  scale_color_solarized()+
  scale_x_continuous(limits = c(0,1)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1)) +
  theme(strip.text.y = element_text(angle = 0))
```

```{r}
# joint model inferred prevalence 
m.samp.targetPrev <- m.samp %>% 
  filter(type == "withinKind") %>% 
  group_by(category, property) %>%
  summarize(MAP = estimate_mode(val),
          cred_upper = hdi_upper(val),
          cred_lower = hdi_lower(val)) %>%
  ungroup() %>% rename(Category = category, Property = property)

left_join(d.prior.summary, 
          m.samp.targetPrev) %>%
  ggplot(., aes(x = MAP, xmin = cred_lower, xmax = cred_upper,
                y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_point()+geom_errorbar(alpha = 0.3)+ geom_errorbarh(alpha = 0.3)+
  scale_x_continuous(limits = c(0, 1))+
  scale_y_continuous(limits = c(0, 1))+
  geom_abline(intercept = 0, slope = 1, lty = 3, alpha = 0.3)+
  coord_fixed()
```

@@

Marginal distributions on prevalence
```{r fig.width = 8, fig.height = 5}
bind_rows(
  d.prior %>% 
  mutate(prevalence = prevalence / 100,
         src = 'data') %>% 
  select(-workerid, -trial_type, -Category),
  m.samp.prevalence.prior %>% 
    rename(Property = property) %>%
    mutate(src = 'model') 
  ) %>%
ggplot(. , aes( x = prevalence, color = src))+
  geom_density(size = 1.1, aes( y = ..scaled.. ))+
  facet_wrap( ~ Property, nrow = 3)+
  scale_color_solarized()+
  scale_x_continuous(limits = c(0,1)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1)) +
  theme(strip.text.y = element_text(angle = 0))
```

@@

```{r fig.width = 8, fig.height = 5}

bind_rows(
  d.prior %>% 
  mutate(prevalence = prevalence / 100,
         src = 'data') %>% 
  select(-workerid, -trial_type, -Category),
  m.samp.prevalence.prior %>% 
    rename(Property = property) %>%
    mutate(src = 'model') 
  ) %>% ggplot(., aes( x = prevalence, color = src))+
    stat_ecdf()+
    facet_wrap(~Property, nrow = 3)+
    scale_color_solarized()+
    scale_x_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
    scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
    theme(strip.text.y = element_text(angle = 0))
```
